A highly-available move operation for replicated trees

### 2019-11-03 paper/move-op.tex
paper: further small addition
paper: a little on future work

Gomes et al.~\cite{Gomes:2017gy} define a framework in Isabelle/HOL for proving the strong eventual consistency properties of CRDTs.
Using our commutativity proof above we integrate our tree datatype with this framework, and thus prove that our move operation on trees does indeed guarantee strong eventual consistency.
The details appear in our Isabelle theory files [URL omitted for blind review]. % \cite{SourceFiles}.

@@

>>>>

Gomes et al.~\cite{Gomes:2017gy} define a framework in Isabelle/HOL for proving the strong eventual consistency properties of CRDTs above an axiomatic network model.
Using our commutativity proof above we integrate our tree datatype with this framework, and thus prove that our move operation on trees does indeed guarantee strong eventual consistency.
The details appear in our Isabelle theory files [URL omitted for blind review]. % \cite{SourceFiles}.

@@

As mentioned in Section~\ref{sec:intro}, the work presented in this paper is especially interesting due to ubiquity of a tree-structured data model.
In future work we hope to build novel peer-to-peer distributed systems, such as a distributed file-system, that make essential use of our algorithm.
